Data preparation B

### 2020-01-14 script/data-prep-B.Rmd
Update data-prep-B.Rmd

```{r}
table(cl19$m2_p13a)
cl19$m2_p13a <- car::recode(cl19$m2_p13a,"c(88,99)=NA",as.numeric = TRUE)
freq(cl19$m2_p13a) # OK esatus subjetivo 2009
dat19$ess <- cl19$m2_p13a # save estatus subjetivo en dat09
freq(dat19$ess)
```

>>>>

```{r}
table(cl19$m2_p13a)
cl19$m2_p13a <- car::recode(cl19$m2_p13a,"c(88,99)=NA",as.numeric = TRUE)
freq(cl19$m2_p13a) # OK esatus subjetivo 2019
dat19$ess <- cl19$m2_p13a # save estatus subjetivo en dat19
freq(dat19$ess)
```
